### 2017-06-09 manuscript.rmd
updated author addresses

Casey W. Dunn^1^*, Felipe Zapata^1,2^, Catriona Munro^1^, Stefan Siebert^1,3^, Andreas Hejnol^4^

@@

^2^ Current address: Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA, USA

^3^ Current address: Department of Molecular & Cellular Biology, University of California at Davis, Davis, CA, USA

>>>>

Casey W. Dunn^1^*, Felipe Zapata^2^, Catriona Munro^1^, Stefan Siebert^3^, Andreas Hejnol^4^

@@

^2^ Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA, USA

^3^ Department of Molecular & Cellular Biology, University of California at Davis, Davis, CA, USA
